Supplementary material to ``\textit{k}-mer-based GWAS enhances the discovery of causal variants and candidate genes in soybean''

### 2023-07-04 additional_files/additional_file_1.tex
Address most of the reviewers' comments

% Defining a command for manhattan plot figures
\newcommand{\manhattanplot}[3]{
	\begin{cfigure}
		\includegraphics[width = 6.5in]{#1_manhattan}
		\caption[Manhattan plots for #2]{Manhattan plots generated from the GWAS analysis of #2 on #3 samples using three genotype datasets :
		(a) Platypus (SNPs and indels), (b) Paragraph (SVs), (c) \emph{k}-mers presence/absence.
		The x-axis shows the position along the reference assembly version 4 of Williams82.
		Each point shows the $-\log_{10} (p)$ associated with a particular marker or \emph{k}-mer.
		Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
		Vertical dotted lines indicate the position of signals associated with the trait.
		Documented loci are colored according to whether they were found (green) or not (red) by a particular approach.
		The ``Gm'' prefix has been left out of chromosome names for simplicity.
		}
		\label{#1_manhattan}
	\end{cfigure}

>>>>

% Defining a command for manhattan plot figures
\newcommand{\manhattanplot}[3]{
	\begin{cfigure}
		\includegraphics[width = 6.5in]{#1_manhattan}
		\caption[Manhattan plots for #2]{Manhattan plots and associated Q-Q plots
		generated from the GWAS analysis of #2 on #3 samples using three genotype datasets :
		(a) Platypus (SNPs and indels), (b) Paragraph (SVs), (c) \emph{k}-mers presence/absence.
		The x-axis shows the position along the reference assembly version 4 of Williams82.
		Each point shows the $-\log_{10} (p)$ associated with a particular marker or \emph{k}-mer.
		Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
		Vertical dotted lines indicate the position of signals associated with the trait.
		Documented loci are colored according to whether they were found (green) or not (red) by a particular approach.
		The ``Gm'' prefix has been left out of chromosome names for simplicity.
		The dashed red line in Q-Q plots represents the identity line ($y = x$)
		}
		\label{#1_manhattan}
	\end{cfigure}
